### 2014-01-31 analysis/Outline.rmd
Biomass fractions for root, leaf stem added to outline.rmd

with(dfr, plot(log_m.so, log_m.lf.fraction, axes=FALSE,
               xlab="Aboveground biomass (kg)",
               ylab="Leaf mass fraction (-)",
               pch=19, col=pft
))
magaxis(side=c(1,2), unlog='xy', tcl=-0.4)
box()
legend("topright", levels(dfr$pft), pch=19, col=palette())

>>>>

with(dfr, plot(log_m.so, log_m.lf.fraction, axes=FALSE,
               xlab="Aboveground biomass (kg)",
               ylab="Leaf mass fraction (-)",
               pch=19, col=pft
))
magaxis(side=c(1,2), unlog='xy', tcl=-0.4)
box()
legend("topright", levels(dfr$pft), pch=19, col=palette())
```

```{r echo=FALSE}
dfr <- droplevels(subset(data, !is.na(m.st) & !is.na(m.lf) & !is.na(m.rt) & 
                           m.lf > 0 & m.rt > 0 & pft != "" & 
                           m.st < m.to))
dfr$m.to <- with(dfr, m.rt + m.st + m.lf)

dfr$dataset <- as.factor(dfr$dataset)
dfr$species <- as.factor(dfr$species)
dfr$pft <- as.factor(dfr$pft)
dfr$m.lf.fraction <- with(dfr, m.lf / m.to)
dfr$m.st.fraction <- with(dfr, m.st / m.to)
dfr$m.rt.fraction <- with(dfr, m.rt / m.to)

par(mfrow=c(2,2))
plotit <- function(Pft, dataset){
  x <- subset(dataset, pft == Pft)
  with(x, plot(log10(m.to), m.rt.fraction, col="red", ylim=c(0,1.1),
               xlab="Total biomass (kg)",
               ylab="Biomass fractions (-)",
               main=Pft,
               axes=FALSE))

  magaxis(side=1, unlog='x', tcl=-0.4)
  axis(2, at=seq(0,1,by=0.2))
  box()
  with(x, points(log10(m.to), m.rt.fraction + m.lf.fraction, col="blue"))
  abline(h=1, lwd=2, col="forestgreen")
}
for(z in c("DA","EA","EG"))plotit(z,dfr)

plot(1, type='n', ann=FALSE, axes=FALSE)
legend("left", c("Root","Root+Leaf","Root+Leaf+Stem"), pch=c(19,19,-1),
                 lty=c(-1,-1,1), col=c("red","blue","forestgreen"), cex=0.8)
```
